---
title: "STA 4320 HW 3"
author: "Mary Robinson"
date: "9/25/24"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

### Part a

Loading data and finding the first six rows
```{r}
# install packages
require(ISLR2)

dat = Auto[1:5]
head(dat)
```


### Part b
Regression Output
```{r}
# reg = lm(mpg ~ cylinders + displacement + horsepower + weight, data = dat)
#or
reg = lm(mpg ~ ., data = dat)
summary(reg)
#percentage of variation in Y is Multiple R-squared value
```


### Part c
Prediction Interval
#for this one we are looking for a SINGLE point (car), so prediction interval instead of confidence interval
```{r}
pred_int = predict(reg, data.frame(cylinders = 6, displacement = 275, horsepower = 125, weight = 3500, interval = "prediction", level = 0.95))
pred_int_rounded = round(as.numeric(pred_int[2:3]))

paste("The prediction interval is ", paste(pred_int_rounded, collapse = " "))
```

### Part d
H0: beta_1 = beta_2 = beta_3 = beta_4 = 0

H1: beta_j is nonzero for at least one of j= 1,2,3,4

The p value to the F Test less than 2.2e^-16. So we reject H0 at the 0.05 level.


### Part e

with the intercept, cylinder, horsepower, and weight already in the model

H0: beta_2 = 0

H1: beta_2 is not equal to 0

(beta_2 is the slope for displacement)

The p value for the T test is 0.9877, way larger than 0.05, so we fail to reject H0.

Thus with the intercept, cylinder, horsepower, and weight already in the model, there is no significant evidence that we should also include displacement.





Once completed, you can compile into pdf if you have LaTeX, or compile to html and then print that html file into a pdf file if you do not have LaTeX. 

### Part f
```{r}
round(cor(dat), 4) 
```


### Part g

full model

```{r}
y= Auto$mpg
n=392
```

RSE= sqrt(RSS / (n-p-1))
RSE: residual standard error

4.242 = sqrt(RSS / (392-4-1))
RSS= 6963.896

Sub model (with onlu horsepower and weight and intercept)
```{r}
reg_0 = lm(mpg ~ horsepower + weight , data= dat)
RSS_0 = sum( ( y-predict(reg_0, data.frame(dat[,c(4,5)])) )^2)
```

compute the test statistic

F_0 = ( (RSS_0 - RSS)/ q) / (RSS/ (n-p-1))
F_0 - (6993.845- 6963.896) / 2) / (6963.896 / (392-4-1))
F_0 = 0.8322

Compute the p value
```{r}
p_val = 1- pf(0.8322, 2, 387 )
p_val
# degrees of freedoms: q=2, n-p-1=392-4-1= 387
```

Make a conclusion 
we fail to reject H0 at the 0.01 level as the pvalue is way larger than 0.01

Therefore, with the intercept, horsepower, and wreight already in the model,
there is insufficient ecidence that we should include cylinders and displacement.



