---
title: "STA 4320 HW 1"
author: "Mary Robinson"
date: "September 18 2024"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

### Part a

Loading Data and Finding the First Six Rows
```{r}
# loading data
library(ISLR2)
require(ISLR2)
```

You can insert more R code chunks 

### Part b

Regression Output
```{r}
y = Auto$mpg
x = Auto$horsepower
reg = lm(y ~ x)
summary(reg)
#could also do: attach(Auto) then summary(lm(mpg ~ horsepower))
```
Answers with words can be typed directly without a code chunk.

### Part c
```{r}
plot(x, y,
     mail = "MPG and Horsepower",
     pch = 16,
     xlab = "Horsepower",
     ylab = "MPG"
)
#can also use Auto$Mpg or horsepower

abline(reg,
       col = "purple",
       lwd = 2)
legend("topright",
       legend = "Regression Line",
       fill = "purple")
```

### Part d

Yes. With the intercept already in the model:

H0: beta_1 vs H1: beta_1 < 0

The pvalue is less than e^-16. So we reject H0 at the 0.05 level.
#pvalue comes from our data t value and we see if it is less than our t value (see pic for details)

### Part e

Yes this is the f test. We can look at the given F-statistic to compare our pvalue with it. 

H0:beta_0 = beta_1 = 0 vs (at least one of the beta_0 or beta_1 is nonzero)

The p value is less than 2.2e^-16 so we reject H0 at the 0.05 level.

### part f

```{r}
newx = data.frame(x = 98)

#simple point
round(as.numeric(predict(reg, newx)), 4)

#confidence interval
round(predict(reg, newx, interval = "confidence", level = 0.95)[-1], 4)

#prediction interval
round(predict(reg, newx, interval = "prediction", level = 0.95)[-1], 4)
```






